---
title: "PSTAT131HW05"
author: "Yifei Zhang"
date: '2022-05-10'
output: pdf_document
toc_float: true
code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE)
```
```{r}
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(klaR)
library(glmnet)
tidymodels_prefer()
Pokemon <- read_csv("Pokemon.csv")
pokemon <- readr::spec(Pokemon)
pokemon
library(janitor)
```


```{r}


```


### Exercise 1

Install and load the `janitor` package. Use its `clean_names()` function on the Pokémon data, and save the results to work with for the rest of the assignment. What happened to the data? Why do you think `clean_names()` is useful?

```{r }
cleaned <- clean_names(Pokemon)
cleaned
```
As the function name suggests, it cleaned the names of our Pokemon data, made the names unique. I think clean_names() is useful, because sometime we may have variables with names that are very similar to each other, and have space as a part of the name, which can cause a lot of problems, and by using clean_names() we can avoid these problems, and we can change the letter case all at once. 


### Exercise 2

Using the entire data set, create a bar chart of the outcome variable, `type_1`.

```{r }
count <- table(cleaned$type_1)
count
barplot(count, xlab = "types", ylab = "counts", main ="type 1 counts")
# not all the type names are shown in the xlab because thats too long
```

How many classes of the outcome are there? Are there any Pokémon types with very few Pokémon? If so, which ones?
    
    There are 18 class of outcomes. There are Pokémon types with very few Pokémon. Such as the  Flying class which only has 4,  Fairy with 17. There are a few other classes that are barely having above 20 pokemons. 

For this assignment, we'll handle the rarer classes by simply filtering them out. Filter the entire data set to contain only Pokémon whose `type_1` is Bug, Fire, Grass, Normal, Water, or Psychic.

```{r }
filtered <- cleaned %>% filter(
  type_1 == "Bug" | type_1 == "Fire" | type_1 == "Grass" 
  |type_1 == " Normal" | type_1 == "Water" | type_1 == "Psychic"
  )
filtered
```

After filtering, convert `type_1` and `legendary` to factors.

```{r }
data <- filtered %>% 
  mutate(type_1 = factor(type_1),
         legendary = factor(legendary),
         generation = factor(generation)
         )
data
```

### Exercise 3

Perform an initial split of the data. Stratify by the outcome variable. You can choose a proportion to use. Verify that your training and test sets have the desired number of observations.

```{r }
pokemon_split <- data %>% 
  initial_split(strata = type_1, prop = 0.7)
pokemon_train <- training(pokemon_split)
pokemon_test <- testing(pokemon_split)
dim(pokemon_train)
```
    
    There are 250 observations in our training set, which is roughly 70 percent of our filtered overall dataset.

Next, use *v*-fold cross-validation on the training set. Use 5 folds. Stratify the folds by `type_1` as well. *Hint: Look for a `strata` argument.* Why might stratifying the folds be useful?

```{r}
pokemon_folds <- vfold_cv(pokemon_train, v = 5, strata = 'type_1')
pokemon_folds

```
  
  Stratifying the folds can be useful useful because we want to make sure the cross validation reaches the result as realistic as possible. 

### Exercise 4

Set up a recipe to predict `type_1` with `legendary`, `generation`, `sp_atk`, `attack`, `speed`, `defense`, `hp`, and `sp_def`.

- Dummy-code `legendary` and `generation`;

- Center and scale all predictors.

```{r }
pokemon_recipe <- recipe(type_1 ~ legendary + generation + sp_atk +
                           attack + speed + defense + hp + sp_def,
                         data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_normalize(all_predictors()) 

```

### Exercise 5

We'll be fitting and tuning an elastic net, tuning `penalty` and `mixture` (use `multinom_reg` with the `glmnet` engine).

Set up this model and workflow. Create a regular grid for `penalty` and `mixture` with 10 levels each; `mixture` should range from 0 to 1. For this assignment, we'll let `penalty` range from -5 to 5 (it's log-scaled).

How many total models will you be fitting when you fit these models to your folded data?

We will be fitting 500 models to our folded data.

```{r }
elastic_spec <- 
  multinom_reg(penalty = tune(), mixture = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("glmnet")

elastic_workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(elastic_spec)

penalty_grid <- grid_regular(penalty(range = c(-5, 5)), 
                             mixture(range = c(0, 1)),
                             levels = 10)
penalty_grid
```

### Exercise 6

Fit the models to your folded data using `tune_grid()`.

Use `autoplot()` on the results. What do you notice? Do larger or smaller values of `penalty` and `mixture` produce better accuracy and ROC AUC?

```{r }
tune_res <- tune_grid(
  elastic_workflow,
  resamples = pokemon_folds, 
  grid = penalty_grid
)
```
```{r }
autoplot(tune_res)

```

### Exercise 7

Use `select_best()` to choose the model that has the optimal `roc_auc`. Then use `finalize_workflow()`, `fit()`, and `augment()` to fit the model to the training set and evaluate its performance on the testing set.

```{r }
collect_metrics(tune_res)
best_penalty <- select_best(tune_res, metric = "roc_auc")
best_penalty
```
```{r}
elastic_final <- finalize_workflow(elastic_workflow, best_penalty)

elastic_final_fit <- fit(elastic_final, data = pokemon_train)


```
augment(elastic_final_fit, new_data = pokemon_test) %>%
  rsq(truth = Salary, estimate = .pred)
  
### Exercise 8

Calculate the overall ROC AUC on the testing set.

Then create plots of the different ROC curves, one per level of the outcome. Also make a heat map of the confusion matrix.

What do you notice? How did your model do? Which Pokemon types is the model best at predicting, and which is it worst at? Do you have any ideas why this might be?


```{r }


```
